Appendix A: Confirmatory LPA for the Caregiver Compass

### 2023-01-24 appendix_a.Rmd
revert MGV previous commit

---
title             : "Appendix A: Confirmatory LPA for the Caregiver Compass"
shorttitle        : "BEST PRACTICES LATENT CLASS ANALYSIS"
bibliography      : "r-references.bib"
floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  markdown: 
    wrap: sentence
---

@@

To load the data, simply attach the `tidySEM` package.
For convenience, we assign the variables used for analysis to an object called `df`.
We first only use the four scales: `c("burdened", "trapped", "negaffect", "loneliness")`.
\`.

@@

```{r echo = TRUE, eval=FALSE, results='asis'}
desc <- tidySEM::descriptives(df)
desc <- desc[, c("name", "n", "missing", "unique",
                 "mean", "median", "sd", "min", "max",
                 "skew_2se", "kurt_2se")]
desc
```

```{r tabdesc, echo = FALSE, eval=TRUE, results='asis'}
desc <- tidySEM::descriptives(df)
desc <- desc[, c("name", "n", "missing", "unique",
                 "mean", "median", "sd", "min", "max",
                 "skew_2se", "kurt_2se")]
papaja::apa_table(desc, caption = "Descriptive statistics")
```

@@

```{r, echo = TRUE, eval = FALSE}
df_plot <- df
names(df_plot) <- paste0("Value.", names(df_plot))
df_plot <- reshape(df_plot, varying = names(df_plot), direction = "long",
                   timevar = "Variable")
ggplot(df_plot, aes(x = Value)) +
  geom_density() +
  facet_wrap(~Variable)+
  theme_bw()
```

```{r, echo = FALSE, eval = run_everything}
# mcartest <- mice::mcar(df)
df_plot <- df
names(df_plot) <- paste0("Value.", names(df_plot))
df_plot <- reshape(df_plot, varying = names(df_plot), direction = "long",
                   timevar = "Variable")
p <- ggplot(df_plot, aes(x = Value)) +
  geom_density() +
  facet_wrap(~Variable)+
  theme_bw()
ggsave("appendices/plot_lpa_desc.pdf", p, device = "pdf", width = 100, height = 100, units = "mm")
```

```{r figdesc, echo = FALSE, eval = pkgdown}
knitr::include_graphics("appendices/plot_lpa_desc.pdf")
```

@@

```{r fitlca, eval = run_everything, echo = FALSE}
set.seed(123) # setting seed 
res <- mx_profiles(data = df,
                   classes = 1:5)
saveRDS(res, "res_lpa.RData")
fit <- table_fit(res)
write.csv(fit, "lpatabfit.csv", row.names = FALSE)
```

```{r eval = FALSE, echo = TRUE}
set.seed(123)
res <- mx_profiles(data = df,
                   classes = 1:5)
```

```{r eval = TRUE, echo = FALSE}
fit <- read.csv("appendices/lpatabfit.csv", stringsAsFactors = FALSE)
class(fit) <- c("tidy_fit", "data.frame")
```

@@

```{r fit_table, include = TRUE, eval=F}
fit <- table_fit(res) # model fit table
fit[ , c("Name", "LL", "Parameters", "n",
         "BIC", "Entropy",
         "prob_min", "prob_max", 
         "n_min", "n_max",
         "lmr_p")]
```

```{r tabfit, echo = FALSE, eval = TRUE}
tbl <- fit[ , c("Name", "LL", "Parameters", "n",
         "BIC", "Entropy",
         "prob_min", "prob_max", 
         "n_min", "n_max",
         "lmr_p")]
names(tbl) <- c("Name", "LL", "p", "n",
         "BIC", "Entropy",
         "p_min", "p_max", 
         "n_min", "n_max",
         "lmr_p")
papaja::apa_table(tbl, caption = "Model fit table")
```

@@

```{r eval = run_everything, echo = FALSE}
res_alt <- mx_profiles(df, classes = 4, variances = "varying")
compare <- list(res[[4]], res_alt)
fit_compare <- table_fit(compare)
write.csv(fit_compare, "lpa_fit_compare.csv", row.names = FALSE)
```

```{r, echo = TRUE, eval = FALSE}
res_alt <- mx_profiles(df, classes = 4, variances = "varying")
compare <- list(res[[4]], res_alt)
table_fit(compare)
```

```{r tabfitcomp, echo = FALSE, eval = TRUE}
fit_compare <- read.csv("appendices/lpa_fit_compare.csv", stringsAsFactors = FALSE)
class(fit_compare) <- c("tidy_fit", "data.frame")
papaja::apa_table(fit_compare[ , c("Name", "LL", "Parameters",
         "BIC", "Entropy",
         "prob_min", "prob_max", 
         "n_min", "n_max")], caption = "Comparing competing theoretical models")
```

@@

```{r, echo = TRUE, eval =FALSE}
res_final <- mx_switch_labels(res[[4]])
```

```{r, echo = FALSE, eval = run_everything}
res_final <- mx_switch_labels(res[[4]])
cp <- class_prob(res_final)
out <- list(counts = cp$sum.posterior$proportion)
```

@@

```{r echo = TRUE, eval = FALSE}
table_results(res_final, columns = c("label", "est", "se", "confint", "class"))
```

```{r echo = FALSE, eval = run_everything}
tab <- table_results(res_final, columns = c("label", "est", "se", "confint", "class"))
write.csv(tab, "lpa_tab_res.csv", row.names = FALSE)
```

```{r, eval = TRUE, echo=FALSE}
tab <- read.csv("appendices/lpa_tab_res.csv", stringsAsFactors = FALSE)
papaja::apa_table(tab, caption = "Four-class model results")
```

@@

```{r echo = TRUE, eval = FALSE}
plot_bivariate(res_final)
```

```{r echo = FALSE, eval = run_everything}
p <- plot_bivariate(res_final, return_list = TRUE)
p[[1]] <- p[[1]] + scale_y_continuous(breaks= c(0, .1, .2, .3), labels = c(".0", ".1", ".2", ".3"))
p <- tidySEM:::merge_corplots(p)
ggsave("appendices/lpa_bivariate.pdf", p, device = "pdf", width = 210, height = 100, units = "mm", scale = 1.5)
```

```{r echo = FALSE, eval = pkgdown, fig.cap="Bivariate profile plot", out.width="100%"}
knitr::include_graphics("appendices/lpa_bivariate.pdf")
```

On the diagonal of the bivariate plot are weighted density plots: normal approximations of the density function of observed data, weighed by class probability.
On the off-diagonal are plots for each pair of indicators, with the class means indicated by a point, class standard deviations indicated by lines, and covariances indicated by circles.
As this model has zero covariances, all circles are round (albeit warped by the different scales of the X and Y axes)

@@

```{r echo = TRUE, eval = FALSE}
plot_profiles(res_final)
```

```{r echo = FALSE, eval = run_everything}
p1 <- plot_profiles(res_final, ci = NULL, sd= FALSE, add_line = TRUE, rawdata = FALSE)
p1 <- p1 + theme(legend.position = c(.85, .2))
p2 <- plot_profiles(res_final)
p2 <- p2 + theme(legend.position = "none")
p <- ggpubr::ggarrange(p1, p2)
ggsave("appendices/lpa_profiles.pdf", p, device = "pdf", width = 210, height = 100, units = "mm", scale = 1)
```

```{r echo = FALSE, eval = pkgdown, fig.cap="Bivariate profile plot", out.width="100%"}
knitr::include_graphics("appendices/lpa_profiles.pdf")
```

@@

```{r echo = TRUE, eval=FALSE}
aux_sex <- BCH(res_final, data = zegwaard_carecompass$sexpatient)
```

```{r echo = FALSE, eval=run_everything}
aux_sex <- BCH(res_final, data = zegwaard_carecompass$sexpatient)
saveRDS(aux_sex, "lpa_aux_sex.RData")
```

```{r echo = FALSE, eval=FALSE}
aux_sex <- readRDS("appendices/lpa_aux_sex.RData")
```

@@

```{r echo = TRUE, eval=FALSE}
df_aux <- zegwaard_carecompass[, c("freqvisit", "distance")]
df_aux$freqvisit <- as.numeric(df_aux$freqvisit)
aux_model <- BCH(res_final, model = "freqvisit ~ distance",
                 data = df_aux)
```

```{r echo = FALSE, eval=run_everything}
df_aux <- zegwaard_carecompass[, c("freqvisit", "distance")]
df_aux$freqvisit <- as.numeric(df_aux$freqvisit)
aux_model <- BCH(res_final, model = "freqvisit ~ distance",
               data = df_aux)
saveRDS(aux_model, "lpa_aux_model.RData")
```

```{r echo = FALSE, eval=FALSE}
aux_model <- readRDS("appendices/lpa_aux_model.RData")
```

@@

@@

<!-- ::: {#refs custom-style="Bibliography"} -->

<!-- ::: -->

## R session

```{r echo = TRUE, eval=TRUE}
sessionInfo()
```

>>>>

---
title             : "Appendix A: Confirmatory LPA for the Caregiver Compass"
shorttitle        : "BEST PRACTICES LATENT CLASS ANALYSIS"

bibliography      : "r-references.bib"

floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

@@

To load the data, simply attach the `tidySEM` package.
For convenience, we assign the variables used for analysis to an object called `df`.
We first only use the four scales: `c("burdened", "trapped", "negaffect", "loneliness")`.
`.

@@

```{r echo = TRUE, eval=FALSE, results='asis'}
desc <- tidySEM::descriptives(df)
desc <- desc[, c("name", "n", "missing", "unique",
                 "mean", "median", "sd", "min", "max",
                 "skew_2se", "kurt_2se")]
desc
```
```{r tabdesc, echo = FALSE, eval=TRUE, results='asis'}
desc <- tidySEM::descriptives(df)
desc <- desc[, c("name", "n", "missing", "unique",
                 "mean", "median", "sd", "min", "max",
                 "skew_2se", "kurt_2se")]
papaja::apa_table(desc, caption = "Descriptive statistics")
```

@@

```{r, echo = TRUE, eval = FALSE}
df_plot <- df
names(df_plot) <- paste0("Value.", names(df_plot))
df_plot <- reshape(df_plot, varying = names(df_plot), direction = "long",
                   timevar = "Variable")
ggplot(df_plot, aes(x = Value)) +
  geom_density() +
  facet_wrap(~Variable)+
  theme_bw()
```
```{r, echo = FALSE, eval = run_everything}
# mcartest <- mice::mcar(df)
df_plot <- df
names(df_plot) <- paste0("Value.", names(df_plot))
df_plot <- reshape(df_plot, varying = names(df_plot), direction = "long",
                   timevar = "Variable")
p <- ggplot(df_plot, aes(x = Value)) +
  geom_density() +
  facet_wrap(~Variable)+
  theme_bw()
ggsave("appendices/plot_lpa_desc.pdf", p, device = "pdf", width = 100, height = 100, units = "mm")
```
```{r figdesc, echo = FALSE, eval = pkgdown}
knitr::include_graphics("appendices/plot_lpa_desc.pdf")
```

@@

```{r fitlca, eval = run_everything, echo = FALSE}
set.seed(123) # setting seed 
res <- mx_profiles(data = df,
                   classes = 1:5)
saveRDS(res, "res_lpa.RData")
fit <- table_fit(res)
write.csv(fit, "lpatabfit.csv", row.names = FALSE)
```
```{r eval = FALSE, echo = TRUE}
set.seed(123)
res <- mx_profiles(data = df,
                   classes = 1:5)
```
```{r eval = TRUE, echo = FALSE}
fit <- read.csv("appendices/lpatabfit.csv", stringsAsFactors = FALSE)
class(fit) <- c("tidy_fit", "data.frame")
```

@@

```{r fit_table, include = TRUE, eval=F}
fit <- table_fit(res) # model fit table
fit[ , c("Name", "LL", "Parameters", "n",
         "BIC", "Entropy",
         "prob_min", "prob_max", 
         "n_min", "n_max",
         "lmr_p")]
```
```{r tabfit, echo = FALSE, eval = TRUE}
tbl <- fit[ , c("Name", "LL", "Parameters", "n",
         "BIC", "Entropy",
         "prob_min", "prob_max", 
         "n_min", "n_max",
         "lmr_p")]
names(tbl) <- c("Name", "LL", "p", "n",
         "BIC", "Entropy",
         "p_min", "p_max", 
         "n_min", "n_max",
         "lmr_p")
papaja::apa_table(tbl, caption = "Model fit table")
```

@@

```{r eval = run_everything, echo = FALSE}
res_alt <- mx_profiles(df, classes = 4, variances = "varying")
compare <- list(res[[4]], res_alt)
fit_compare <- table_fit(compare)
write.csv(fit_compare, "lpa_fit_compare.csv", row.names = FALSE)
```
```{r, echo = TRUE, eval = FALSE}
res_alt <- mx_profiles(df, classes = 4, variances = "varying")
compare <- list(res[[4]], res_alt)
table_fit(compare)
```
```{r tabfitcomp, echo = FALSE, eval = TRUE}
fit_compare <- read.csv("appendices/lpa_fit_compare.csv", stringsAsFactors = FALSE)
class(fit_compare) <- c("tidy_fit", "data.frame")
papaja::apa_table(fit_compare[ , c("Name", "LL", "Parameters",
         "BIC", "Entropy",
         "prob_min", "prob_max", 
         "n_min", "n_max")], caption = "Comparing competing theoretical models")
```

@@

```{r, echo = TRUE, eval =FALSE}
res_final <- mx_switch_labels(res[[4]])
```
```{r, echo = FALSE, eval = run_everything}
res_final <- mx_switch_labels(res[[4]])
cp <- class_prob(res_final)
out <- list(counts = cp$sum.posterior$proportion)
```

@@

```{r echo = TRUE, eval = FALSE}
table_results(res_final, columns = c("label", "est", "se", "confint", "class"))
```
```{r echo = FALSE, eval = run_everything}
tab <- table_results(res_final, columns = c("label", "est", "se", "confint", "class"))
write.csv(tab, "lpa_tab_res.csv", row.names = FALSE)
```
```{r, eval = TRUE, echo=FALSE}
tab <- read.csv("appendices/lpa_tab_res.csv", stringsAsFactors = FALSE)
papaja::apa_table(tab, caption = "Four-class model results")
```

@@

```{r echo = TRUE, eval = FALSE}
plot_bivariate(res_final)
```
```{r echo = FALSE, eval = run_everything}
p <- plot_bivariate(res_final, return_list = TRUE)
p[[1]] <- p[[1]] + scale_y_continuous(breaks= c(0, .1, .2, .3), labels = c(".0", ".1", ".2", ".3"))
p <- tidySEM:::merge_corplots(p)
ggsave("appendices/lpa_bivariate.pdf", p, device = "pdf", width = 210, height = 100, units = "mm", scale = 1.5)
```
```{r echo = FALSE, eval = pkgdown, fig.cap="Bivariate profile plot", out.width="100%"}
knitr::include_graphics("appendices/lpa_bivariate.pdf")
```
On the diagonal of the bivariate plot are weighted density plots:
normal approximations of the density function of observed data,
weighed by class probability.
On the off-diagonal are plots for each pair of indicators,
with the class means indicated by a point,
class standard deviations indicated by lines,
and covariances indicated by circles.
As this model has zero covariances,
all circles are round (albeit warped by the different scales of the X and Y axes)

@@

```{r echo = TRUE, eval = FALSE}
plot_profiles(res_final)
```
```{r echo = FALSE, eval = run_everything}
p1 <- plot_profiles(res_final, ci = NULL, sd= FALSE, add_line = TRUE, rawdata = FALSE)
p1 <- p1 + theme(legend.position = c(.85, .2))
p2 <- plot_profiles(res_final)
p2 <- p2 + theme(legend.position = "none")
p <- ggpubr::ggarrange(p1, p2)
ggsave("appendices/lpa_profiles.pdf", p, device = "pdf", width = 210, height = 100, units = "mm", scale = 1)
```
```{r echo = FALSE, eval = pkgdown, fig.cap="Bivariate profile plot", out.width="100%"}
knitr::include_graphics("appendices/lpa_profiles.pdf")
```

@@

```{r echo = TRUE, eval=FALSE}
aux_sex <- BCH(res_final, data = zegwaard_carecompass$sexpatient)
```
```{r echo = FALSE, eval=run_everything}
aux_sex <- BCH(res_final, data = zegwaard_carecompass$sexpatient)
saveRDS(aux_sex, "lpa_aux_sex.RData")
```
```{r echo = FALSE, eval=FALSE}
aux_sex <- readRDS("appendices/lpa_aux_sex.RData")
```

@@

```{r echo = TRUE, eval=FALSE}
df_aux <- zegwaard_carecompass[, c("freqvisit", "distance")]
df_aux$freqvisit <- as.numeric(df_aux$freqvisit)
aux_model <- BCH(res_final, model = "freqvisit ~ distance",
                 data = df_aux)
```
```{r echo = FALSE, eval=run_everything}
df_aux <- zegwaard_carecompass[, c("freqvisit", "distance")]
df_aux$freqvisit <- as.numeric(df_aux$freqvisit)
aux_model <- BCH(res_final, model = "freqvisit ~ distance",
               data = df_aux)
saveRDS(aux_model, "lpa_aux_model.RData")
```
```{r echo = FALSE, eval=FALSE}
aux_model <- readRDS("appendices/lpa_aux_model.RData")
```

@@

<!-- \newpage -->

@@

<!-- ::: {#refs custom-style="Bibliography"} -->
<!-- ::: -->

### 2023-01-24 appendix_a.tex
revert MGV previous commit

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Load required packages}
\FunctionTok{library}\NormalTok{(tidySEM) }
\FunctionTok{library}\NormalTok{(ggplot2)}
\CommentTok{\# Load data}
\NormalTok{df }\OtherTok{\textless{}{-}}\NormalTok{ zegwaard\_carecompass[, }\FunctionTok{c}\NormalTok{(}\StringTok{"burdened"}\NormalTok{, }\StringTok{"trapped"}\NormalTok{, }\StringTok{"negaffect"}\NormalTok{, }\StringTok{"loneliness"}\NormalTok{)]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{desc }\OtherTok{\textless{}{-}}\NormalTok{ tidySEM}\SpecialCharTok{::}\FunctionTok{descriptives}\NormalTok{(df)}
\NormalTok{desc }\OtherTok{\textless{}{-}}\NormalTok{ desc[, }\FunctionTok{c}\NormalTok{(}\StringTok{"name"}\NormalTok{, }\StringTok{"n"}\NormalTok{, }\StringTok{"missing"}\NormalTok{, }\StringTok{"unique"}\NormalTok{,}
                 \StringTok{"mean"}\NormalTok{, }\StringTok{"median"}\NormalTok{, }\StringTok{"sd"}\NormalTok{, }\StringTok{"min"}\NormalTok{, }\StringTok{"max"}\NormalTok{,}
                 \StringTok{"skew\_2se"}\NormalTok{, }\StringTok{"kurt\_2se"}\NormalTok{)]}
\NormalTok{desc}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_plot }\OtherTok{\textless{}{-}}\NormalTok{ df}
\FunctionTok{names}\NormalTok{(df\_plot) }\OtherTok{\textless{}{-}} \FunctionTok{paste0}\NormalTok{(}\StringTok{"Value."}\NormalTok{, }\FunctionTok{names}\NormalTok{(df\_plot))}
\NormalTok{df\_plot }\OtherTok{\textless{}{-}} \FunctionTok{reshape}\NormalTok{(df\_plot, }\AttributeTok{varying =} \FunctionTok{names}\NormalTok{(df\_plot), }\AttributeTok{direction =} \StringTok{"long"}\NormalTok{,}
                   \AttributeTok{timevar =} \StringTok{"Variable"}\NormalTok{)}
\FunctionTok{ggplot}\NormalTok{(df\_plot, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Value)) }\SpecialCharTok{+}
  \FunctionTok{geom\_density}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Variable)}\SpecialCharTok{+}
  \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\NormalTok{res }\OtherTok{\textless{}{-}} \FunctionTok{mx\_profiles}\NormalTok{(}\AttributeTok{data =}\NormalTok{ df,}
                   \AttributeTok{classes =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{table\_results}\NormalTok{(res\_final, }\AttributeTok{columns =} \FunctionTok{c}\NormalTok{(}\StringTok{"label"}\NormalTok{, }\StringTok{"est"}\NormalTok{, }\StringTok{"se"}\NormalTok{, }\StringTok{"confint"}\NormalTok{, }\StringTok{"class"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_aux }\OtherTok{\textless{}{-}}\NormalTok{ zegwaard\_carecompass[, }\FunctionTok{c}\NormalTok{(}\StringTok{"freqvisit"}\NormalTok{, }\StringTok{"distance"}\NormalTok{)]}
\NormalTok{df\_aux}\SpecialCharTok{$}\NormalTok{freqvisit }\OtherTok{\textless{}{-}} \FunctionTok{as.numeric}\NormalTok{(df\_aux}\SpecialCharTok{$}\NormalTok{freqvisit)}
\NormalTok{aux\_model }\OtherTok{\textless{}{-}} \FunctionTok{BCH}\NormalTok{(res\_final, }\AttributeTok{model =} \StringTok{"freqvisit \textasciitilde{} distance"}\NormalTok{,}
                 \AttributeTok{data =}\NormalTok{ df\_aux)}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{r-session}{%
\subsection{R session}\label{r-session}}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{sessionInfo}\NormalTok{()}
\CommentTok{\#\textgreater{} R version 4.1.3 (2022{-}03{-}10)}
\CommentTok{\#\textgreater{} Platform: x86\_64{-}w64{-}mingw32/x64 (64{-}bit)}
\CommentTok{\#\textgreater{} Running under: Windows 10 x64 (build 19045)}
\CommentTok{\#\textgreater{} }
\CommentTok{\#\textgreater{} Matrix products: default}
\CommentTok{\#\textgreater{} }
\CommentTok{\#\textgreater{} locale:}
\CommentTok{\#\textgreater{} [1] LC\_COLLATE=English\_United Kingdom.1252 }
\CommentTok{\#\textgreater{} [2] LC\_CTYPE=English\_United Kingdom.1252   }
\CommentTok{\#\textgreater{} [3] LC\_MONETARY=English\_United Kingdom.1252}
\CommentTok{\#\textgreater{} [4] LC\_NUMERIC=C                           }
\CommentTok{\#\textgreater{} [5] LC\_TIME=English\_United Kingdom.1252    }
\CommentTok{\#\textgreater{} }
\CommentTok{\#\textgreater{} attached base packages:}
\CommentTok{\#\textgreater{} [1] stats     graphics  grDevices utils     datasets  methods   base     }
\CommentTok{\#\textgreater{} }
\CommentTok{\#\textgreater{} other attached packages:}
\CommentTok{\#\textgreater{} [1] ggplot2\_3.4.0    tidySEM\_0.2.4.6  OpenMx\_2.21.1    scales\_1.2.1    }
\CommentTok{\#\textgreater{} [5] yaml\_2.3.6       papaja\_0.1.1     tinylabels\_0.2.3}
\CommentTok{\#\textgreater{} }
\CommentTok{\#\textgreater{} loaded via a namespace (and not attached):}
\CommentTok{\#\textgreater{}   [1] TH.data\_1.1{-}1         colorspace\_2.1{-}0      estimability\_1.4.1   }
\CommentTok{\#\textgreater{}   [4] parameters\_0.20.1     rstudioapi\_0.14       listenv\_0.9.0        }
\CommentTok{\#\textgreater{}   [7] lavaan\_0.6{-}13         rstan\_2.26.13         fansi\_1.0.4          }
\CommentTok{\#\textgreater{}  [10] mvtnorm\_1.1{-}3         codetools\_0.2{-}18      splines\_4.1.3        }
\CommentTok{\#\textgreater{}  [13] mnormt\_2.1.1          knitr\_1.41            texreg\_1.38.6        }
\CommentTok{\#\textgreater{}  [16] bayesplot\_1.10.0      jsonlite\_1.8.4        effectsize\_0.8.2     }
\CommentTok{\#\textgreater{}  [19] compiler\_4.1.3        httr\_1.4.4            emmeans\_1.8.4{-}1      }
\CommentTok{\#\textgreater{}  [22] backports\_1.4.1       assertthat\_0.2.1      Matrix\_1.5{-}3         }
\CommentTok{\#\textgreater{}  [25] fastmap\_1.1.0         cli\_3.6.0             htmltools\_0.5.4      }
\CommentTok{\#\textgreater{}  [28] prettyunits\_1.1.1     tools\_4.1.3           igraph\_1.3.5         }
\CommentTok{\#\textgreater{}  [31] coda\_0.19{-}4           gtable\_0.3.1          glue\_1.6.2           }
\CommentTok{\#\textgreater{}  [34] RANN\_2.6.1            dplyr\_1.0.10          V8\_4.2.2             }
\CommentTok{\#\textgreater{}  [37] Rcpp\_1.0.10           carData\_3.0{-}5         vctrs\_0.5.2          }
\CommentTok{\#\textgreater{}  [40] nlme\_3.1{-}161          psych\_2.2.9           insight\_0.18.8       }
\CommentTok{\#\textgreater{}  [43] xfun\_0.36             stringr\_1.5.0         globals\_0.16.2       }
\CommentTok{\#\textgreater{}  [46] ps\_1.7.2              proto\_1.0.0           CompQuadForm\_1.4.3   }
\CommentTok{\#\textgreater{}  [49] lifecycle\_1.0.3       future\_1.30.0         MASS\_7.3{-}58.2        }
\CommentTok{\#\textgreater{}  [52] zoo\_1.8{-}11            parallel\_4.1.3        sandwich\_3.0{-}2       }
\CommentTok{\#\textgreater{}  [55] inline\_0.3.19         curl\_5.0.0            gridExtra\_2.3        }
\CommentTok{\#\textgreater{}  [58] pander\_0.6.5          blavaan\_0.4{-}3         loo\_2.5.1            }
\CommentTok{\#\textgreater{}  [61] StanHeaders\_2.26.13   stringi\_1.7.12        highr\_0.10           }
\CommentTok{\#\textgreater{}  [64] bayestestR\_0.13.0     fastDummies\_1.6.3     checkmate\_2.1.0      }
\CommentTok{\#\textgreater{}  [67] boot\_1.3{-}28           pkgbuild\_1.4.0        rlang\_1.0.6          }
\CommentTok{\#\textgreater{}  [70] pkgconfig\_2.0.3       matrixStats\_0.63.0    evaluate\_0.20        }
\CommentTok{\#\textgreater{}  [73] lattice\_0.20{-}45       rstantools\_2.2.0      processx\_3.8.0       }
\CommentTok{\#\textgreater{}  [76] tidyselect\_1.2.0      parallelly\_1.34.0     plyr\_1.8.8           }
\CommentTok{\#\textgreater{}  [79] magrittr\_2.0.3        bookdown\_0.32         R6\_2.5.1             }
\CommentTok{\#\textgreater{}  [82] generics\_0.1.3        multcomp\_1.4{-}20       DBI\_1.1.3            }
\CommentTok{\#\textgreater{}  [85] withr\_2.5.0           gsubfn\_0.7            pillar\_1.8.1         }
\CommentTok{\#\textgreater{}  [88] survival\_3.5{-}0        datawizard\_0.6.5      abind\_1.4{-}5          }
\CommentTok{\#\textgreater{}  [91] tibble\_3.1.8          future.apply\_1.10.0   crayon\_1.5.2         }
\CommentTok{\#\textgreater{}  [94] car\_3.1{-}1             nonnest2\_0.5{-}5        utf8\_1.2.2           }
\CommentTok{\#\textgreater{}  [97] tmvnsim\_1.0{-}2         MplusAutomation\_1.1.0 rmarkdown\_2.20       }
\CommentTok{\#\textgreater{} [100] grid\_4.1.3            data.table\_1.14.6     pbivnorm\_0.6.0       }
\CommentTok{\#\textgreater{} [103] bain\_0.2.8            callr\_3.7.3           digest\_0.6.31        }
\CommentTok{\#\textgreater{} [106] xtable\_1.8{-}4          dbscan\_1.1{-}11         RcppParallel\_5.1.6   }
\CommentTok{\#\textgreater{} [109] stats4\_4.1.3          munsell\_0.5.0}
\end{Highlighting}
\end{Shaded}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Load required packages}
\FunctionTok{library}\NormalTok{(tidySEM)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\CommentTok{\# Load data}
\NormalTok{df }\OtherTok{\textless{}{-}}\NormalTok{ zegwaard\_carecompass[, }\FunctionTok{c}\NormalTok{(}\StringTok{"burdened"}\NormalTok{, }\StringTok{"trapped"}\NormalTok{, }\StringTok{"negaffect"}\NormalTok{,}
    \StringTok{"loneliness"}\NormalTok{)]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{desc }\OtherTok{\textless{}{-}}\NormalTok{ tidySEM}\SpecialCharTok{::}\FunctionTok{descriptives}\NormalTok{(df)}
\NormalTok{desc }\OtherTok{\textless{}{-}}\NormalTok{ desc[, }\FunctionTok{c}\NormalTok{(}\StringTok{"name"}\NormalTok{, }\StringTok{"n"}\NormalTok{, }\StringTok{"missing"}\NormalTok{, }\StringTok{"unique"}\NormalTok{, }\StringTok{"mean"}\NormalTok{, }\StringTok{"median"}\NormalTok{,}
    \StringTok{"sd"}\NormalTok{, }\StringTok{"min"}\NormalTok{, }\StringTok{"max"}\NormalTok{, }\StringTok{"skew\_2se"}\NormalTok{, }\StringTok{"kurt\_2se"}\NormalTok{)]}
\NormalTok{desc}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_plot }\OtherTok{\textless{}{-}}\NormalTok{ df}
\FunctionTok{names}\NormalTok{(df\_plot) }\OtherTok{\textless{}{-}} \FunctionTok{paste0}\NormalTok{(}\StringTok{"Value."}\NormalTok{, }\FunctionTok{names}\NormalTok{(df\_plot))}
\NormalTok{df\_plot }\OtherTok{\textless{}{-}} \FunctionTok{reshape}\NormalTok{(df\_plot, }\AttributeTok{varying =} \FunctionTok{names}\NormalTok{(df\_plot), }\AttributeTok{direction =} \StringTok{"long"}\NormalTok{,}
    \AttributeTok{timevar =} \StringTok{"Variable"}\NormalTok{)}
\FunctionTok{ggplot}\NormalTok{(df\_plot, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Value)) }\SpecialCharTok{+} \FunctionTok{geom\_density}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Variable) }\SpecialCharTok{+}
    \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\NormalTok{res }\OtherTok{\textless{}{-}} \FunctionTok{mx\_profiles}\NormalTok{(}\AttributeTok{data =}\NormalTok{ df, }\AttributeTok{classes =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{table\_results}\NormalTok{(res\_final, }\AttributeTok{columns =} \FunctionTok{c}\NormalTok{(}\StringTok{"label"}\NormalTok{, }\StringTok{"est"}\NormalTok{, }\StringTok{"se"}\NormalTok{, }\StringTok{"confint"}\NormalTok{,}
    \StringTok{"class"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_aux }\OtherTok{\textless{}{-}}\NormalTok{ zegwaard\_carecompass[, }\FunctionTok{c}\NormalTok{(}\StringTok{"freqvisit"}\NormalTok{, }\StringTok{"distance"}\NormalTok{)]}
\NormalTok{df\_aux}\SpecialCharTok{$}\NormalTok{freqvisit }\OtherTok{\textless{}{-}} \FunctionTok{as.numeric}\NormalTok{(df\_aux}\SpecialCharTok{$}\NormalTok{freqvisit)}
\NormalTok{aux\_model }\OtherTok{\textless{}{-}} \FunctionTok{BCH}\NormalTok{(res\_final, }\AttributeTok{model =} \StringTok{"freqvisit \textasciitilde{} distance"}\NormalTok{, }\AttributeTok{data =}\NormalTok{ df\_aux)}
\end{Highlighting}
\end{Shaded}

@@
